### 2024-04-19 docs/SOSP 2024/reduction.tex
Change titles to save space
Use ttfamily for snippets

\section{Reductions : Representation, Optimization and Lowering}
\label{sec:reduction}
\Treebeard{} needs to sum up individual tree predictions to compute 
the prediction of the model while performing inference. However,
generating fused reductions within arbitrary loop nests specified 
using \Treebeard{}'s scheduling language is non-trivial. We found 
that existing reduction support in MLIR is insufficient to code
generate and optimize these reductions. MLIR only supports reductions
of value types and does not provide ways to lower reductions to GPUs. 
To address this gap, we design an MLIR dialect that allows us to
specify accumulating values into an element of a multi-dimensional array
and can be lowered to CPU or GPU.

@@

\begin{lstlisting}[style=c++]
  float result[batch_size], partResults[2][batch_size]
  model = ensemble(...) 
  par.for t0 = 0 to N_t step N_t/2:
    for t1 = 0 to N_t/2:
      for batch = 0 to batch_size:
        t = getTree(model, t0 + t1) 
        p = walkDecisionTree(t, rows[batch])
        reduce(partResults[t0/(N_t/2)][batch], p)

>>>>

\section{Representing and Optimizing Reductions}
\label{sec:reduction}
\Treebeard{} needs to sum up individual tree predictions to compute 
the prediction of the model while performing inference. However,
generating fused reductions within arbitrary loop nests specified 
using \Treebeard{}'s scheduling language is non-trivial. We found 
that existing reduction support in MLIR is insufficient to code
generate and optimize these reductions. MLIR only supports reductions
of value types and does not provide ways to lower reductions to GPUs. 
To address this gap, we design an MLIR dialect that allows us to
specify accumulating values into an element of a multi-dimensional array
and can be lowered to CPU or GPU.

@@

\begin{lstlisting}[style=c++]
  float result[batch_size];
  float partResults[2][batch_size];
  model = ensemble(...) 
  par.for t0 = 0 to N_t step N_t/2:
    for t1 = 0 to N_t/2:
      for batch = 0 to batch_size:
        t = getTree(model, t0 + t1) 
        p = walkDecisionTree(t, rows[batch])
        reduce(partResults[t0/(N_t/2)][batch], p)
